% narrative_2026-06-12.tex — hand-authored case-study sections for the
% 2026-06-12 verification run report. Included by gen-compute-report.mjs via
% --narrative=. Every number below traces to a job id, a git SHA, or a Cloud
% Run revision named in the text. British spelling; measured register.

\section{The deployment chain}
This run closed a release cycle that moved the engine's public registry from
23 to 26 methods. Three registrations landed together: \code{namh\_pipeline}
(a seeded end-to-end surrogate pipeline run as an asynchronous workstation
job), \code{namh\_reproduce} (a $\Delta$-verifier that re-runs the published
NAMH estimators and reports the maximum absolute deviation from the paper's
archived output), and \code{soch\_robustness} (a badge-mode stability grid
over the published SOCH-B symmetry test, the subject of
Section~\ref{sec:case}).

The chain was: engine push (commits \code{37d4337..5d0dc80}, with the
post-fix commit \code{f1616f2} following), source deploy to Cloud Run
revision \code{shssm-compute-00033-wq2}, an environment-variable restore to
revision \code{00034-zqz}, and --- after the driver fix described below --- a
second deploy arriving at revision \code{shssm-compute-00036-llf}, which this
report's suite ran against. Two operational details are worth the record.
First, the deploy script's API-key lookup missed because the repository had
moved; the documented remedy (an in-place service update, no rebuild)
restored chat capability in under a minute, and the miss was loudly warned by
the script itself --- a designed failure surface behaving as designed.
Second, the suite's single-shot 15-second health probe once recorded a live
engine as unreachable while all 26 method rows passed against it: the probe
had raced a Cloud Run cold start. The probe now retries once with a longer
window; the dead-engine path (a deliberately unreachable URL must produce a
non-zero exit and honest red rows) still passes.

\section{Case study: a stochastic gate caught by its own evaluation}
\label{sec:case}
The most instructive event of the run was a failure. The
\code{soch\_robustness} row re-runs the published SOCH-B direction-symmetry
test (the \code{sochcontagion} package's own \code{soch\_test\_symmetry},
GPL-3 --- the paper's code, not a reimplementation) over a nuisance grid
$\tau \in \{0.05, 0.10\} \times J \in \{4, 5\}$ on the eight advanced markets
(28 unordered pairs per configuration, 112 grid points), with a
200-replication bootstrap null. Its expected band was pre-registered from the
Phase-31 closure board: the baseline cell ($\tau=0.05$, $J=4$) holds
$28/28$ pairs --- the paper's ground truth --- with an overall pass rate of
at least $0.90$.

The first genuine end-to-end execution of this driver returned $27/28$ at
baseline and an overall pass rate of $0.9821$ ($110/112$), and the row went
red. Investigation showed the driver carried no random-number-generator pin:
the bootstrap null's 95th-percentile threshold was stochastic across runs,
and one near-boundary pair sat close enough to its threshold to flip between
executions. The Phase-31 grid run had measured $0.9911$ ($111/112$) --- one
grid point away --- consistent with the same knife edge landing on the other
side.

The repair followed the engine's existing seeded-determinism precedent
(\code{namh\_pipeline}): the driver now pins \code{RNGkind("L'Ecuyer-CMRG")}
with seed 42 \cite{lecuyer1999}, and reports both in its output. The band
was not touched. A fresh anchor run (job \code{job\_20260612\_fe0c4f06},
773.5\,s) returned baseline $28/28$, pass rate $0.9911$, badge
\emph{robust} --- the paper's ground truth and the Phase-31 measurement
reproduced exactly under the pin. The full suite was then re-run from
scratch, and its independently submitted job
(\code{job\_20260612\_c0398d0f}) returned the identical tuple, digit for
digit: two independent executions now verify determinism end to end. The
evaluation row was tightened, not widened --- it now requires the exact
seeded pass rate ($0.9911$), the exact baseline count ($28/28$), and the
seed itself ($42$) to be echoed in the result.

Three points generalise beyond this engine. First, binary bootstrap-gated
claims of the form ``the pair holds symmetry'' sit on resampling knife edges
at modest replication counts; at $B=200$, a single marginal pair is enough to
move a headline count. A reproducibility statement for such a claim is
meaningful only with the full tuple --- seed, generator, replication count,
filter, grid, and market set --- stated. Second, grid resolution bounds the
interpretability of badge rates: with 112 points, one flip moves the rate by
$1/112 \approx 0.0089$, so $0.9821$ versus $0.9911$ is a one-point
difference, not a qualitative change; counts should accompany rates. Third,
the institutional lesson: the gate that failed was not noise to be routed
around but the system working --- a pre-registered band over a first-run
driver surfaced a latent nondeterminism that would otherwise have produced
intermittent, unexplainable reds in nightly operation.

\section{Formal and epistemic layers}
Two verification layers beyond the numerical suite are active. The formal
layer (Lean~4 with mathlib, toolchain v4.30.0) machine-checks the SOCH
spectral results: 11 of 12 declarations are Lean-accepted, including the
unconditional closure of the product-Lorentzian spectral density
proposition ($\Vert H(\omega)\Vert^{2} = S(\omega)$) and an
existence-and-uniqueness chain for the first-order-condition frequency; one
declaration (the analytic half of the peak-location lemma) honestly carries
\code{sorry} and is reported as unproved. The epistemic layer --- a
provenance-carrying claims ledger with twenty seeded claims spanning
established, contested, and superseded states --- is built and its public
read surface is deployed; its data store provisioning remains a gated
operator action, and until it runs the API degrades honestly, naming the
missing dataset rather than fabricating an empty success.

\section{Implications}
For applied work, the run's substantive anchors held without exception:
the India ADF statistic ($-49.18$), the GARCH persistence ($\alpha + \beta =
0.991$), the named-panel IPS statistic ($-77.26$ on
\{India, USA, UK, China, Japan\}), the NAMH transfer-entropy window mean
($-0.22322165$, inside its pre-registered band), the KSG USA$\to$Japan
transfer entropy ($0.154$), the KSG robustness Spearman ($0.7282$), the
GFC trade-channel share ($27.9\%$, arXiv:2604.26546), and the live systemic
risk index ($0.00849$). The honest negatives also held: the FDR-gated NAMH
network retains $0/552$ edges and is reported as a degenerate network
(amber), and the SOCH-C significance test remains not significant
($p=0.105$) --- both immutable facts of the record, not blemishes to be
managed. The engine's claim is not that its numbers are impressive but that
they are traceable: every figure in this report resolves to a job
identifier, a revision string, or a published artefact, and the pipeline
that produced this document will produce the next one unattended.

\section*{Addendum (2026-06-13): GPU offload of the transfer-entropy search}
\label{sec:gpu}
The heaviest asynchronous methods in this run, \code{ksg\_te} and
\code{ksg\_robustness}, spend their time in an $O(n^2)$ nearest-neighbour
search under the Chebyshev norm --- the Kraskov--Stoegbauer--Grassberger /
Frenzel--Pompe transfer-entropy estimator. On the workstation this work had a
latent failure mode: the drivers hard-coded \code{detectCores()-1} mclapply
workers and ignored the job's core request, so two concurrent robustness jobs
forked forty-two workers over twenty-two logical cores with unpinned
multi-threaded BLAS beneath them, pinned every core at $100\%$, and hung the
machine mid-pipeline. That oversubscription was first removed at source --- a
single governed core budget, clamped last by a server-set hard ceiling, on
every fork site --- which makes the CPU path safe. The complementary step,
recorded here, is to move the search off the CPU altogether.

The same primitive now runs on the workstation's NVIDIA RTX 3000 Ada GPU
through \code{numba.cuda}, a path that needed no new installation (the CUDA
toolkit and \code{numba} were already present). The two methods dispatch to
the GPU when a CUDA device is visible and fall back to the governed CPU path
otherwise; a single environment switch forces the CPU path when wanted. The
bar was the engine's standing reproduce-integrity rule: the GPU must
\emph{equal} the CPU, not approximate it. The observed transfer entropy --- the
only quantity the evaluation suite gates --- is held bit-exact. A dedicated
gate measured a maximum absolute deviation of $7\times10^{-16}$ between the GPU
and the engine's own CPU estimator (the six-decimal emitted figures identical)
across embedding lags $\{1,2\}$ and neighbour counts $\{4,5\}$. The gate also
surfaced a genuine floating-point subtlety worth recording: the engine's
one-dimensional neighbour count tests membership through the subtraction
$v-\varepsilon$ rather than $|\Delta|<\varepsilon$, and so admits a boundary
point that the textbook strict form rejects when $|\Delta|$ rounds to exactly
$\varepsilon$. The GPU path was made to reproduce the engine's behaviour, not
the textbook's, because the published figure --- not the cleaner derivation ---
is the anchor a regression must protect.

Significance is unchanged in distribution. Neither transfer-entropy method
seeds a generator, so the IAAFT surrogate $p$-value is a non-reproducible draw
in both the CPU and GPU paths; the surrogate construction was vectorised into a
batched Fourier transform on the host, and a pair's observed estimate together
with all ninety-nine of its surrogates now executes as one batched device
launch, so that the per-launch and transfer overhead is paid once per pair
rather than once per surrogate.

The test that matters is the workload that hung the machine, re-run on the new
path: the full eighteen-market panel, all $306$ directed pairs, ninety-nine
IAAFT surrogates each --- $30{,}600$ neighbour searches. It completed in
$35.6$ minutes at $100\%$ of a \emph{single} core (peak resident set
$388$\,MB), against a measured $289$\,s for a twelve-pair slice on the governed
CPU path across roughly seven cores, which extrapolates to about two hours for
the full panel: the GPU path is some $3.5\times$ faster while leaving the
processor --- and the other twenty-one cores --- free for concurrent work. The
substantive result is unmoved. The headline link, USA$\to$Japan, returns
transfer entropy $0.154234$ to the digit; $106$ of $306$ directed links are
significant at $p<0.05$; and the strongest flows are all \emph{into} Japan ---
from the United States ($0.1542$), Germany ($0.1108$), Canada ($0.1075$) and
France ($0.1030$) --- recovering the same information-sink structure the CPU
path reports, now as a by-product of a run that no longer threatens the host.

Two points generalise. First, when a published estimator is ported to a faster
device, the equivalence test must be written against the estimator's own
output, including its floating-point boundary conventions, rather than against
the form in which it is usually written down; the device that is ``more
correct'' is the wrong device if it moves a number the literature has already
recorded. Second, massively parallel fan-out belongs on hardware built for it
--- a GPU's thousands of lanes --- rather than on an unbounded CPU fork that
competes with every other job on the machine; the same arithmetic that
saturated twenty-two cores now occupies one core and a few hundred megabytes of
video memory, and runs faster for it.
