\section{The methodological substrate and the method registry}
\label{sec:substrate}

The engine's claim to be a single substrate, rather than a bag of scripts, rests on
one observation. The six published frameworks it carries (NAMH, SOCH,
contagion-channels, WaveQTE, the commodity study, and MCPFM) do not each need a
private toolchain. They are recombinations of a small number of estimator-level
operations: measure how a series remembers its own past, split its variance across
time scales, quantify directed information flow, build a null by surrogate
construction, partition a network into communities, decompose a system's
connectedness, attribute a transmitted shock to a structural channel, and validate
a binary call against a curve. We call these the \emph{eight primitives}. Every one
of the \textbf{26} registry methods is one or more primitives wired to a dataset,
and every method ships with a pre-registered, failable test of its own output. The
registered voice is deliberate: we would rather have twenty-six checked methods than
fifty asserted ones.

This section names the eight primitives and their mathematical objects
(\S\ref{sec:primitives}), shows how the registry's six families map onto them
(\S\ref{sec:registry}), then gives the transfer-entropy estimator in full because it
is the load-bearing one and the only quantity the GPU path must reproduce bit-for-bit
(\S\ref{sec:ksg}). We close with the determinism discipline that makes the estimators
reproducible (\S\ref{sec:determinism}) and the failable-test rule that governs
catalogue entry (\S\ref{sec:failable}).

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  prim/.style={draw=ceblue, thick, fill=ceblue!10, rounded corners=1pt, align=left,
    inner sep=3pt, text width=3.0cm, font=\scriptsize, minimum height=6.4mm},
  fw/.style={draw=ceorange, thick, fill=ceorange!12, rounded corners=1pt, align=center,
    inner sep=3pt, text width=2.8cm, font=\footnotesize, minimum height=7.5mm},
  edge/.style={draw=cegrey!50, line width=0.4pt}]
  \node[prim] (P1) at (0,7.0) {P1\, long memory (DFA/GPH)};
  \node[prim] (P2) at (0,6.0) {P2\, MODWT wavelets};
  \node[prim] (P3) at (0,5.0) {P3\, transfer entropy};
  \node[prim] (P4) at (0,4.0) {P4\, surrogates (IAAFT)};
  \node[prim] (P5) at (0,3.0) {P5\, community (Leiden)};
  \node[prim] (P6) at (0,2.0) {P6\, network (DY)};
  \node[prim] (P7) at (0,1.0) {P7\, channel attrib.\ (IV)};
  \node[prim] (P8) at (0,0.0) {P8\, ROC / DeLong};
  \node[fw] (NAMH) at (7.0,6.3) {NAMH};
  \node[fw] (SOCH) at (7.0,5.1) {SOCH};
  \node[fw] (CC)   at (7.0,3.9) {contagion-channels};
  \node[fw] (WQ)   at (7.0,2.7) {WaveQTE};
  \node[fw] (CM)   at (7.0,1.5) {commodity};
  \node[fw] (MC)   at (7.0,0.3) {MCPFM};
  \begin{scope}[on background layer]
    \foreach \p in {P1,P3,P4,P5,P6} \draw[edge] (\p.east) -- (NAMH.west);
    \foreach \p in {P2,P3}          \draw[edge] (\p.east) -- (SOCH.west);
    \foreach \p in {P2,P3,P5,P7}    \draw[edge] (\p.east) -- (CC.west);
    \foreach \p in {P2,P3,P4}       \draw[edge] (\p.east) -- (WQ.west);
    \foreach \p in {P3,P5,P6}       \draw[edge] (\p.east) -- (CM.west);
    \foreach \p in {P2,P6,P8}       \draw[edge] (\p.east) -- (MC.west);
  \end{scope}
\end{tikzpicture}
\caption{The substrate carries the programme. Each published framework (right,
in orange) composes a subset of the eight estimator-level primitives (left, in
blue); the same transfer-entropy and network machinery recurs across elements.
The composition shown is the principal-primitive view; Section~\ref{sec:elements}
gives each element in full.}
\label{fig:substrate}
\end{figure}

\subsection{The eight primitives}
\label{sec:primitives}

Table~\ref{tab:primitives} names each primitive, the mathematical object it returns,
its canonical reference, and the registry methods that instantiate it. The primitives
are estimator-level, not framework-level: a single method (for example
\method{namh\_pipeline}) composes several, and a single primitive (for example P3) is
shared across frameworks that otherwise have nothing in common.

\begin{table}[t]
\centering
\footnotesize
\caption{The eight-primitive substrate. Each primitive is an estimator-level
operation with a fixed mathematical object and a canonical reference; the registry
methods in the last column instantiate it on a whitelisted dataset.}
\label{tab:primitives}
\begin{tabular}{@{}p{2.25cm}p{4.5cm}p{2.7cm}p{4.55cm}@{}}
\toprule
\textbf{Primitive} & \textbf{Object computed} & \textbf{Reference} & \textbf{Example methods} \\
\midrule
P1 long-memory &
  Hurst exponent $H$; $\phi(H)=1-2|H-\tfrac12|$ &
  DFA / GPH / Qu &
  \method{dfa\_hurst}, \method{namh\_hurst} \\
P2 multi-scale &
  MODWT detail variance $\{\sigma^2_{d_j}\}$ &
  \cite{barunik2018} &
  \method{wavelet}, \method{wavelet\_coherence} \\
P3 information flow &
  directed TE $T_{Y\to X}$ &
  \cite{schreiber2000,kraskov2004,frenzel2007} &
  \method{ksg\_te}, \method{namh\_te}, \method{wqte} \\
P4 surrogate null &
  IAAFT / permutation null distribution &
  \cite{schreiber1996} &
  \method{ksg\_te}, \method{namh\_pipeline} \\
P5 community &
  partition / modularity $Q$ &
  \cite{traag2019} &
  \method{network}, \method{namh\_pipeline} \\
P6 connectedness &
  GFEVD spillover; frequency bands &
  \cite{diebold2012,diebold2014,barunik2018} &
  \method{connectedness}, \method{spillover\_rolling} \\
P7 channel attribution &
  per-channel share via IV / 2SLS &
  \cite{bhandari2026contagion} &
  \method{channel\_attribution} \\
P8 ROC validation &
  AUC; DeLong / Hansen test &
  \cite{bhandari2025mcpfm} &
  MCPFM out-of-sample call \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{P1 -- long memory.}
The object is the Hurst exponent $H$, the scaling exponent of detrended fluctuation
analysis. On the cumulative profile $y_t=\sum_{s\le t}(x_s-\bar x)$ the series is cut
into log-spaced boxes, each box is detrended by a local polynomial, the
root-mean-square residual fluctuation $F(n)$ is taken per box length $n$, and $H$ is
the slope of $\log F(n)$ on $\log n$. The transparent realisation
(\file{r/dfa\_hurst.R}) implements this directly; the published path
(\file{r/namh\_hurst.R}) calls \method{namh::estimate\_hurst\_panel}
\citep{namhpkg} on a rolling window and supplies the NAMH node weight
$\phi(H)=1-2|H-\tfrac12|$, a local-efficiency score peaking at the random-walk value
$H=\tfrac12$. We read $H$ on log-returns, which are $I(0)$, never on price levels,
which are $I(1)$.

\paragraph{P2 -- multi-scale decomposition.}
The object is the variance of a series across dyadic time scales, obtained from the
maximal-overlap discrete wavelet transform (MODWT). Boundary-affected coefficients
are removed by the \method{brick.wall} operator before the per-scale variance
$\sigma^2_{d_j}$ is read, so scale $d_1$ corresponds to roughly $2$--$4$ day
fluctuations, $d_2$ to $4$--$8$ days, and so on (\file{r/wavelet.R}). The same
decomposition underlies the scale-resolved squared coherence
$\rho^2_j=\mathrm{cor}(d^x_j,d^y_j)^2$ (\file{r/wavelet\_coherence.R}), which we label
honestly as a discrete scale-resolved coherence rather than the continuous Morlet
time-frequency object. P2 is the Stage-1 primitive of NAMH, MCPFM, and the
contagion-channels frameworks.

\paragraph{P3 -- directed information flow.}
The object is transfer entropy $T_{Y\to X}$, the reduction in uncertainty about
$X_{t+1}$ from knowing the past of $Y$ beyond the past of $X$ \citep{schreiber2000}.
Three estimators sit under this primitive: the engine's own
Kraskov--St{\"o}gbauer--Grassberger / Frenzel--Pompe $k$-nearest-neighbour estimator
(\method{ksg\_te}, derived in full in \S\ref{sec:ksg}); the published \method{namh}
package's Euclidean RANN variant (\method{namh\_te}); and a transparent
wavelet-quantile measure built from MODWT and quantile regression (\method{wqte}).
These are different estimators of the same object and their magnitudes are not
cross-comparable, a boundary the runners state explicitly.

\paragraph{P4 -- surrogate construction.}
The object is a null distribution for a dependence statistic, built without parametric
assumptions. The engine's default is the iterative amplitude-adjusted Fourier
transform (IAAFT) of \citet{schreiber1996}: a surrogate of the source series is formed
by alternately imposing the source's Fourier amplitude spectrum and its empirical
amplitude distribution until the rank order stabilises, so the surrogate preserves the
source's linear autocorrelation and marginal while destroying its (possibly nonlinear)
predictive dependence on the target. Significance of a directed TE edge is then
$p=(1+\#\{T^{\text{surr}}\ge T^{\text{obs}}\})/(B+1)$. Surrogate subtraction also
defines \emph{effective} transfer entropy (\S\ref{sec:ksg}).

\paragraph{P5 -- community detection.}
The object is a partition of a directed weighted network into communities, with a
modularity score $Q$. The published NAMH pipeline uses the Leiden algorithm
\citep{traag2019}, which guarantees well-connected communities and corrects the
resolution-limit pathologies of Louvain; the transparent \method{network} surface uses
a Walktrap partition on the undirected projection of a Granger graph. A community
result is only as meaningful as the adjacency it partitions: when the upstream FDR
gate retains no edges, the partition is degenerate by construction and is reported as
such, not dressed up.

\paragraph{P6 -- connectedness and network formation.}
The object is a system's total and directional connectedness from a vector
autoregression's generalised forecast-error variance decomposition (GFEVD). The
time-domain index is Diebold--Y{\i}lmaz \citep{diebold2012,diebold2014}; the
frequency decomposition is Barun{\'i}k--K{\v r}ehl{\'i}k \citep{barunik2018}, which
splits the total connectedness index across short ($\le 5$ day), medium ($5$--$20$
day), and long ($>20$ day) bands by partitioning the spectral GFEVD at
$\omega=2\pi/P$ (\file{r/connectedness.R}). The rolling variant
(\method{spillover\_rolling}) tracks the index through time.

\paragraph{P7 -- structural channel attribution.}
The object is the share of a transmitted shock attributable to each of a fixed set of
economic channels, identified with instruments rather than read off a reduced-form
correlation. The published contagion-channels pipeline
\citep{bhandari2026contagion,ccpkg} runs a two-stage detection-and-attribution
procedure: Stage 1 detects directed tail linkages, Stage 2 attributes them to five
mutually exclusive channels (trade, financial, geopolitical, behavioural, monetary)
by instrumental-variables / two-stage least squares (\file{r/channel\_attribution.R}).
This is the primitive that turns a network edge into an economic explanation.

\paragraph{P8 -- ROC validation.}
The object is the area under the receiver-operating-characteristic curve (AUC) of a
binary forecast, with a significance test on the AUC. This is the primitive by which a
predictive claim is held to account out of sample; MCPFM \citep{bhandari2025mcpfm}
reports AUC with a DeLong test in version 1 and, under a pre-registered
re-evaluation, a Hansen superior-predictive-ability test in version 2. We report both
openly (\S\ref{sec:failable}).

\subsection{The registry and its six families}
\label{sec:registry}

The \textbf{26} methods are grouped into six families by the statistical question they
answer, not by which primitives they happen to share; a family is the unit a reader
reasons about, while a primitive is the unit the code reuses. Table~\ref{tab:families}
gives the family structure with a representative method or two from each, its
primitive composition, and one verified value. The complete per-method registry with
every pre-registered acceptance band is Appendix~A; here we show only the shape.

\begin{table}[t]
\centering
\footnotesize
\caption{The six families of the registry (26 methods total), with a representative
method per family, the substrate primitives it composes, and one verified value. The
full per-method acceptance bands are in Appendix~A. Counts: stationarity 5, volatility
5, information flow 5, connectedness 6, contagion 2, reproduction 3.}
\label{tab:families}
\begin{tabular}{@{}p{4.2cm}p{3.8cm}p{1.5cm}p{4.7cm}@{}}
\toprule
\textbf{Family ($n$)} & \textbf{Representative method} & \textbf{Primitives} & \textbf{Verified value} \\
\midrule
Stationarity, cointegration, panels (5) &
  \method{panel\_unit\_root}, \method{vecm} & -- &
  IPS $-77.26$; Johansen rank 3 \\
Volatility, long memory, spectra (5) &
  \method{dfa\_hurst}, \method{wavelet} & P1, P2 &
  India $H=0.542$; $d_1=47.07\%$ \\
Information flow (5) &
  \method{ksg\_te}, \method{wqte} & P3, P4 &
  USA$\to$Japan TE $0.154234$ \\
Connectedness, networks (6) &
  \method{connectedness}, \method{network} & P5, P6 &
  TCI $30.25\%$; density $0.5667$ \\
Contagion, systemic risk (2) &
  \method{channel\_attribution}, \method{sri\_daily} & P5, P7 &
  GFC trade $27.9\%$ \\
Reproduction, formal verification (3) &
  \method{namh\_reproduce}, \method{soch\_robustness} & P1--P5 &
  $\max|\Delta|\,1.55\times10^{-15}$ \\
\bottomrule
\end{tabular}
\end{table}

Two points the table cannot show. First, the families are not silos: the same
estimator can appear in several. Transfer entropy (P3) is the engine of the
information-flow family, but it is also the first stage of the NAMH pipeline in the
reproduction family. Second, a method may be either a \emph{transparent} realisation
built from substrate parts, or a \emph{published} method that calls a paper's own
package directly. \method{wqte} reimplements the WaveQTE Stage-1 primitive from
\method{waveslim} and \method{quantreg} because the packaged estimator does not load
in the image; \method{soch\_profile}, \method{channel\_attribution},
\method{namh\_hurst}, and \method{namh\_te} call \method{sochcontagion}, \method{contagionchannels},
and \method{namh} respectively, so the live engine runs the paper's own code. The
distinction is recorded on every such method, because a transparent reimplementation
and a bit-exact package call carry different reproduction claims.

\subsection{The transfer-entropy estimator in full}
\label{sec:ksg}

Transfer entropy is the load-bearing primitive: it is the most-used edge statistic in
the programme, the one quantity the GPU path must reproduce bit-for-bit, and the one
whose estimator subtleties most repay a careful statement. We give it here at the
depth of the implementation in \file{r/\_ksg\_core.R} and \file{gpu/ksg\_gpu.py}.

\paragraph{Transfer entropy as conditional mutual information.}
For an ordered pair $(Y\to X)$ with history length (lag) $\ell$, transfer entropy is
the conditional mutual information between the one-step future of the target and the
past of the source, given the past of the target \citep{schreiber2000}:
\begin{equation}
\label{eq:te-cmi}
T_{Y\to X} \;=\; I\!\left(X_{t+1}\,;\, Y_t^{(\ell)} \;\middle|\; X_t^{(\ell)}\right),
\qquad
Y_t^{(\ell)} = \bigl(Y_t, Y_{t-1}, \dots, Y_{t-\ell+1}\bigr).
\end{equation}
The conditioning set $Z = X_t^{(\ell)}$ is the target's own past; the marginal blocks
are $X = X_{t+1}$ (the future, dimension $1$) and $Y = Y_t^{(\ell)}$ (the source past,
dimension $\ell$). The engine's default is $\ell=1$ (\method{ksg\_te} parameter
\code{lag}), the Markov-1 conditioning under which the past blocks collapse to the
single lagged values $X_t$ and $Y_t$. The embedding aligns the future $X_{t+1}$ with
the lag blocks ending at $t$, so that one point of the joint sample is
$(X_{t+1}, Y_t^{(\ell)}, X_t^{(\ell)})$.

\paragraph{The KSG / Frenzel--Pompe estimator.}
Rather than bin the joint density, the estimator counts neighbours. Following
\citet{kraskov2004} for mutual information and \citet{frenzel2007} for its conditional
extension, the conditional mutual information in Eq.~\eqref{eq:te-cmi} is estimated by
\begin{equation}
\label{eq:ksg-cmi}
\widehat{I}(X;Y\mid Z) \;=\; \psi(k)
  \;+\; \frac{1}{N}\sum_{i=1}^{N}\Bigl[\,
    \psi\!\bigl(n^Z_i+1\bigr) - \psi\!\bigl(n^{XZ}_i+1\bigr) - \psi\!\bigl(n^{YZ}_i+1\bigr)
  \,\Bigr],
\end{equation}
where $\psi$ is the digamma function, $k$ is the neighbour count (parameter \code{k},
default $4$), and $N$ is the number of embedded points. The three counts are taken in
the marginal sub-spaces of the conditioning set and its unions with each variable:
$n^Z_i$, $n^{XZ}_i$, $n^{YZ}_i$ count the points whose distance from point $i$ in the
$Z$, $(X,Z)$, and $(Y,Z)$ sub-spaces respectively is strictly less than $\epsilon_i$.
This is the \method{.ksg\_cmi} function; the transfer entropy
$T_{Y\to X}=\widehat{I}$ at $Z=X_t^{(\ell)}$ is \method{.te}.

\paragraph{The max-norm and the neighbour radius.}
The metric is the maximum (Chebyshev) norm,
\begin{equation}
\label{eq:maxnorm}
\Norm{u-v}_\infty \;=\; \max_{c} \,\lvert u_c - v_c \rvert,
\end{equation}
taken over all coordinates of the relevant space. The radius $\epsilon_i$ is the
max-norm distance from point $i$ to its $k$-th nearest neighbour in the \emph{full}
joint space $(X,Y,Z)$, self excluded. The engine works in raw return coordinates and
does not standardise, because the G20 series are already daily log-returns and the
max-norm is not scale-invariant, so a $z$-score would change the estimate; the runners
and the GPU helper both note this. Computing $\epsilon_i$ exactly under the max-norm on
a tree built for the Euclidean norm uses the inclusion $\Norm{\cdot}_\infty \le
\Norm{\cdot}_2 \le \sqrt{d}\,\Norm{\cdot}_\infty$: an inflated $L_2$ candidate list is
pulled, exact Chebyshev distances are recomputed, the $k$-th smallest is taken, and a
point's radius is accepted only once its candidate list provably covers that radius
(\method{.maxnorm\_knn\_dist}). This makes the radius exact, not approximate.

\paragraph{The one-dimensional count boundary.}
A subtlety the bit-exactness gate caught, and which a careful reader should know about,
lives in how the strict-inequality counts are realised. For a sub-space of dimension
$\ge 2$ the count is taken directly as $\#\{j\neq i : \Norm{u_i-u_j}_\infty <
\epsilon_i\}$ by recomputing the max-norm and applying $<$ (\method{.count\_kd}). For a
one-dimensional sub-space (which arises for the $Z$ count when $\ell=1$) the engine
uses a sorted-array realisation via \method{findInterval}
(\method{.count\_1d}), testing membership against the half-open interval
$[v-\epsilon,\, v+\epsilon)$ rather than the absolute form $|v_j-v|<\epsilon$. The two
disagree on exactly one floating-point boundary tie: when $|v_j-v|$ rounds to exactly
$\epsilon$ but $v-\epsilon$ rounds down, the interval form \emph{includes} the point
that the absolute form rejects. The engine's choice is the \method{.count\_1d}
convention, and the GPU helper reproduces that convention host-side rather than the
textbook absolute form (\file{gpu/ksg\_gpu.py}, \method{\_count\_1d\_engine\_batch}),
so the observed estimate matches the engine's own six-decimal emission exactly. The
lesson, recorded as a learning, is to gate on the estimator's own output including its
floating-point boundary conventions, not on the textbook formula.

\paragraph{Effective transfer entropy.}
The raw estimate of Eq.~\eqref{eq:ksg-cmi} carries a finite-sample bias that does not
vanish under the null of no information flow. Following the surrogate bias-correction
of \citet{marschinski2002}, the \emph{effective} transfer entropy subtracts the mean of
the estimator over surrogate source series that share the source's marginal and linear
autocorrelation but carry no directed dependence on the target:
\begin{equation}
\label{eq:ete}
T^{\text{eff}}_{Y\to X}
  \;=\; T_{Y\to X} \;-\; \frac{1}{B}\sum_{b=1}^{B} T_{\,\tilde Y^{(b)}\to X},
\qquad \tilde Y^{(b)} \sim \text{IAAFT}(Y),
\end{equation}
with $B$ surrogates drawn by the IAAFT of \S\ref{sec:primitives}. The same surrogate
ensemble gives the permutation $p$-value $p=(1+\#\{T_{\tilde Y\to X}\ge
T_{Y\to X}\})/(B+1)$. The published NAMH pipeline computes
Eq.~\eqref{eq:ete} explicitly (\method{TE\_eff} in \file{r/namh\_pipeline.R}); the
deterministic \method{namh\_te} method returns the raw estimate only and states that
the effective TE and the $p$-values, being surrogate-dependent and unseeded in the
package, are not bit-reproducible and belong to the async pipeline.

\paragraph{GPU equivalence on the observed estimate.}
The cost is an $O(N^2)$ max-norm neighbour search, once per directed pair and once per
surrogate, which previously saturated the workstation. The search now runs on the
RTX 3000 Ada GPU through two \method{numba.cuda} kernels (one for the radii, one for
the three counts), with the IAAFT surrogates batched on the host
(\file{gpu/ksg\_gpu.py}). Crucially, the \emph{observed} transfer entropy is the only
quantity the evaluation suite gates, and it is held bit-exact to the CPU estimator:
the measured maximum discrepancy is $7\times10^{-16}$ and the six-decimal emission is
identical, across $\ell\in\{1,2\}$ and $k\in\{4,5\}$, verified by
\file{gpu/equiv\_gate.R}. The $p$-value is an unseeded surrogate draw in both the CPU
and GPU paths and is never claimed reproducible. Defaulting to the GPU therefore can
never move a published number; a box with no CUDA device, or a forced \code{CE\_GPU=0},
degrades silently to the governed CPU path.

\subsection{Determinism and reproducibility of the estimators}
\label{sec:determinism}

Reproducibility of a Monte-Carlo estimator requires that two facts be pinned: the
random stream, and the order of reduction. The engine pins both.

\paragraph{The random stream.}
Where a method's result depends on a draw, the runner sets
\code{RNGkind("L'Ecuyer-CMRG")} and \code{set.seed(42)} before the computation. The
combined multiple-recursive generator of \citet{lecuyer1999} is chosen because it
splits into independent sub-streams that \method{parallel::mclapply} can hand to its
fork workers deterministically: under a fixed seed each child stream derives
reproducibly from the master seed. The canonical surrogate count is $B=200$. The
published NAMH end-to-end run is the clearest case (\file{r/namh\_pipeline.R}): the
\method{namh} package's own IAAFT generator is unseeded, so the paper's published
surrogate run is not bit-reproducible; the engine's runner pins the seed and the
generator so that its result \emph{is} reproducible for a fixed
$\{\text{seed}, n_{\text{cores}}\}$ pair. That dependence on the core count, through
the stream split, is stated rather than hidden. The two \method{ksg} methods are
deliberately \emph{not} seeded, so their surrogate $p$-values are an honest
non-reproducible draw in both the CPU and GPU paths; their reproducible content is the
observed TE, which carries no randomness.

\paragraph{The order-free reduction.}
The directed-pair and grid loops are order-free: the result is a set of per-pair
estimates reduced by operations (sums, means, rank correlations, set overlaps) that do
not depend on the order in which the pairs complete. This is what lets the worker
count be governed without touching a number. The shared helper
\method{ce\_ncores} in \file{r/\_io.R} sets the \method{mclapply} budget from a base of
\code{detectCores()} minus a reserve, overridden by an explicit \code{n\_cores}, and
clamped last by a hard ceiling \code{CE\_MAX\_CORES} (which the tower sets to
$\lfloor(\text{cpus}-2)/\text{MAX\_CONCURRENT}\rfloor=10$ on the workstation). BLAS
threading is pinned to one thread per spawn. Because the loops are order-free, changing
the worker count from one to ten never changes a TE value; it only governs CPU. This is
the formal content of an invariant the system depends on.

\begin{invariant}[Worker-count neutrality]
\label{inv:order-free}
For every method that reduces a set of independently computed per-pair or per-grid
estimates, the emitted result is invariant to the number of parallel workers and to the
order in which they complete. Core governance and BLAS pinning therefore change CPU
occupancy, never a published value.
\end{invariant}

\subsection{A failable test per method}
\label{sec:failable}

The discipline that makes the registry trustworthy is one rule, applied without
exception.

\begin{principle}[Catalogue entry requires a failable test]
\label{prin:failable}
A method enters the registry only with a pre-registered, failable acceptance band on
its own output, fixed before the run. A regression turns the public dashboard red
rather than passing silently; a hole is marked, never filled; and the band is never
edited to fit a result.
\end{principle}

Three verified examples show the principle at work, drawn from
Table~\ref{tab:families} and the registry. They are stated with their provenance, in
the registered measured voice, because a real number with a band is worth more than an
adjective.

\begin{cexample}[An observed estimate in band]
\label{ex:ksg}
The \method{ksg\_te} method on the 18-market G20 panel returns the USA$\to$Japan
transfer entropy as $\mathbf{0.154234}$, across $306$ directed pairs of which $108$ are
significant at $p<0.05$ against IAAFT source surrogates. The pre-registered band is
$T\in[0.150,0.158]$; the value sits inside it. The same observed estimate is the
quantity the GPU path reproduces to $7\times10^{-16}$, and a full-panel re-run of all
$306$ pairs reproduced $0.154234$ exactly.
\end{cexample}

\begin{cexample}[A stability claim across nuisance parameters]
\label{ex:robustness}
The \method{ksg\_robustness} sweep re-runs the same estimator across the grid
$k\in\{3,4,6,8\}\times\ell\in\{1,2\}$ and checks two pre-registered conditions: that the
headline directed edge is ranked first at every grid point, and that the mean Spearman
rank correlation of the full directed-TE vector against the baseline lies in
$[0.6,0.85]$. Both hold: the mean Spearman is $\mathbf{0.7282}$ (minimum $0.581$), and
USA$\to$Japan is the \#1 directed edge across all eight $(k,\ell)$ settings. The
headline link is therefore robust to the estimator's nuisance parameters, not an
artefact of one choice.
\end{cexample}

\begin{cexample}[A published estimate held to a tight band]
\label{ex:namh}
The \method{namh\_hurst} method, running the published \method{namh} package on its
rolling-window panel, returns a mean Hurst exponent for Gold of $\mathbf{0.490}$
($0.4899$). The pre-registered band is $[0.4889,0.4909]$, a tight window that would
fail loudly on any drift in the package or the data. The value is reproduced to
$\max|\Delta|\,1.55\times10^{-15}$ same-machine by the \method{namh\_reproduce}
$\Delta$-verifier.
\end{cexample}

Honest negatives are themselves results under Principle~\ref{prin:failable} and are
immutable facts of the record, not failures to be hidden. The MCPFM out-of-sample call
returns AUC $0.581$ (DeLong $p=0.030$) in version 1; a pre-registered version-2
re-evaluation returns AUC $0.470$ (Hansen SPA $p=0.031$), and that lower figure is
reported openly with a reproduce status of honest-pending. The NAMH pipeline's own
Benjamini--Hochberg FDR gate retains $0/552$ directed edges at the canonical
configuration, so its masked network, fixed point, and communities are degenerate by
construction and are emitted as measured, in the dashboard's honest amber, rather than
magnitude-dressed. A method that asserted a clean network there would be the failure;
reporting the empty gate is the discipline.
