\section{The AI layer: a natural-language client, not a privileged path}
\label{sec:ai-layer}

The engine is reachable in plain language. A researcher can ask a question -- ``is the
UK equity series stationary?'', ``which market sends the most information to Japan?''
-- and receive an answer that ran the real econometrics rather than a plausible
paragraph. Two routes provide this. \route{/api/chat} is a fast analyst backed by
Gemini 2.5 Flash; \route{/api/research} is a deeper assistant backed by Gemini 2.5 Pro
that both runs analyses and grounds its synthesis in literature. The design problem
they pose is not capability but containment: a language model that can trigger compute
is a new way to reach the engine, and we must be sure it is not a new way to reach
anything else. The whole of this section is organised around the claim that it is not,
because the AI layer is a client of the engine on exactly the same footing as a script
or a web form, with no execution surface of its own.

\subsection{The chat route}
\label{sec:chat-route}

\route{/api/chat} is a single function-calling turn followed by a summary. The user's
message goes to Gemini with one tool, \method{run\_analysis}, whose parameters are a
method name and its typed arguments; the model either answers conceptually with no tool
call or emits exactly one call. That call is not executed as written. It is passed
through the same \method{validate} routine every other caller uses -- which rejects an
unknown method or a mistyped parameter -- and only the validated, cleaned method and
arguments reach \method{runSandboxed}. The result is then handed back to the model for
a second turn that explains the numbers in prose. The route returns
\code{\{reply, ran\}}, where \code{ran} records the method, the cleaned parameters, the
raw result, and the wall time, so the natural-language answer is always accompanied by
the machine record it was built from. The system prompt is a careful econometrician,
not a generic assistant; in particular it carries the stationarity rule discussed
below, so the model never reports a price level as stationary.

\subsection{The research route}
\label{sec:research-route}

\route{/api/research} is the same idea at publication depth, and it runs in two phases.
Phase~A is an agentic loop, bounded to a few steps, in which Gemini 2.5 Pro is given
the \method{run\_analysis} tool and runs live econometrics wherever the question admits
it -- it may issue several calls, see their results, and call again, each call passing
through the same \method{validate} and \method{runSandboxed} path as the chat route.
Phase~B is a grounded synthesis: the analyses executed in Phase~A are summarised into a
digest, the digest and the question are sent back to the model with a
\code{google\_search} tool, and the model writes the final answer grounded in real
sources. The route returns
\[
  \texttt{\{answer,\ citations[],\ searches[],\ analyses[],\ steps\}},
\]
so the caller receives the prose answer, the grounding citations (title and URI), the
search queries the model issued, the full record of every analysis it ran, and the
step count. The citations are read from the model's grounding metadata, not invented by
the prose.

The two phases are kept separate for a concrete reason of API behaviour rather than
preference. Function-calling and \code{google\_search} grounding are not reliably
combined within one Gemini request, so the engine does not attempt to. Instead it runs
the tools in their own passes and carries the executed analyses forward as text into
the grounded pass; the model still cites real literature \emph{and} reasons over real
live numbers, but the two tool modes never share a single request. This is the kind of
fragility a systems report should name: the separation is a workaround for a model-API
constraint, documented in the route itself.

The system prompt for the research route does substantial work, and all of it is fact,
not flourish. It injects the eight-primitive substrate -- long-memory estimation,
MODWT wavelet decomposition, transfer entropy, surrogate inference, community
detection, network-formation game theory, structural attribution, and classifier
validation -- so the model reasons in the engine's own vocabulary; it names the
frameworks those primitives instantiate; and it injects the verified-results table
verbatim with the instruction to quote it exactly and never alter it, so a number the
model states is a number the engine has checked. It also carries the stationarity rule
as an inviolable constraint.

\begin{principle}[The stationarity rule]
\label{prin:stationarity}
Transfer entropy and the other dependence measures are estimated on $I(0)$ log-returns,
never on $I(1)$ price levels. Equity price levels carry a unit root (a random walk with
drift); log-returns, $\mathrm{diff}(\log \text{price})$, are typically stationary. The
stored G20 panel is already log-returns, so any ``stationary'' verdict over it concerns
returns, and the model is required to say so explicitly (``UK equity \emph{returns} are
stationary'', not ``the UK market is stationary''). Embedding this rule in the prompt
prevents the most common and most consequential error an unguided model would make on
financial series.
\end{principle}

\subsection{The safety argument}
\label{sec:ai-safety}

The reason the AI layer can be exposed at all is that it adds no power. Everything it
can cause to happen, a direct caller of \route{/api/compute/run} could already cause to
happen; everything a direct caller cannot do, the AI layer cannot do either. This is
worth stating precisely, because it is the load-bearing claim of the whole design.

\begin{invariant}[The AI layer is a client, not a privileged path]
\label{inv:ai-client}
The model cannot execute arbitrary code. It can only name a method already in the
registry and supply typed parameters for it, and it can only read that method's
returned result. Its proposed call is validated by the same \method{validate} routine
and executed by the same \method{runSandboxed} path as any other request, so it
inherits every guard those impose and introduces no new execution surface. The
registry of parameterised methods is the boundary; the language model sits outside it,
on the same side as a script or a browser.
\end{invariant}

This follows directly from the implementation. A function call from Gemini is data: a
method string and an arguments object. It is subjected to \method{validate} before it
is allowed to mean anything, and \method{validate} is the same gate the public compute
route uses, so an attempt to name a method that does not exist, or to pass a parameter
of the wrong type or shape, is rejected before any R process is spawned. There is no
path by which the model can supply code, a file path, a shell fragment, or a network
target; the parameterised-only registry that is the engine's primary guard against
arbitrary execution applies to the model exactly as it applies to everyone else. The
AI layer widens the engine's audience -- it makes the methods reachable by people who
would not write the JSON by hand -- without widening its attack surface.

\subsection{Rate limits and the cost bound}
\label{sec:ai-cost}

Because each model turn costs real money, the AI routes are bounded on several axes, and
the bound that matters most is a hard ceiling on spend rather than a courtesy throttle.
The per-IP limiter caps \route{/api/research} at roughly five requests per minute and
roughly twenty per day, with \route{/api/chat} held to a higher but still bounded rate;
these stop a single client from monopolising the service or slowly draining the credit.
Above those sits the ceiling that bounds the worst case regardless of how many clients
attack at once. Each instance permits at most $400$ paid LLM turns per UTC day, and
Cloud Run is configured for at most two instances, so the fleet-wide maximum is
\[
  400 \ \text{turns/instance/day} \times 2 \ \text{instances}
  \;=\; \textbf{at most 800 paid turns/day}.
\]
The day counter resets at UTC midnight, and when the cap is reached the routes return a
service-unavailable response with a retry hint rather than paying for another turn. The
limiter is process-local and resets on restart, which is acceptable precisely because
the per-instance daily cap multiplied by the instance ceiling already gives a bounded
fleet-wide daily maximum: the AI layer cannot, under any traffic pattern, spend more
than that.
