\section{Verification and Epistemics}
\label{sec:verification}

The engine's claim to trustworthiness does not rest on the authors' assurance.
It rests on a small set of machine-run artefacts that any reader can inspect and,
given the repository, re-execute: a pre-registered evaluation suite that grades
live computation against failable numerical bands, a nightly loop that re-runs
that suite and writes its own findings into a ledger it does not get to edit by
hand, a claims record that demotes rather than deletes, and a thin formal layer
in which one identity is closed in a proof assistant with an honest count of what
remains open. This section describes those four artefacts and the single property
that ties them together: the apparatus is built so that its own correctness, and
the wiring that enforces it, are themselves things that can fail a test in public.

\subsection{The evaluation suite}
\label{sec:verification-evals}

The suite lives in \file{evals/run-evals.mjs} and emits a single artefact,
\file{evals.json}. Each catalogue method has exactly one row. A row names the
method, the parameter object it is called with, an \code{expected} string stating
the pre-registered band in plain language, a \code{source} citing where that band
comes from, and a \code{check} function that extracts one quantity from the live
result and returns a boolean. The runner posts the request to the deployed engine
(or, for the four heavy asynchronous methods, submits a real job to the
workstation job server and polls it to completion), applies the check, and records
the verdict. It computes; it does not read a cached number. The most recent full
run recorded \textbf{26 of 26 rows passing} (0 fail, 0 pending) against the live
service.

Three rules govern the artefact, and each is enforced by construction rather than
by convention.

\begin{principle}[Bands are pre-registered and failable]
A band is fixed before the run, from a documented verified value, and is written
so that the result can fall outside it. Where a method's verified tuple does not
pin a full configuration, the band degrades to an invariant check that can still
fail on the wrong shape, a non-finite value, an unstable system, or a wrong
verdict, never to a check that always passes.
\end{principle}

\begin{principle}[The artefact is never hand-edited]
\file{evals.json} is the output of one genuine execution of the committed runner.
A red row is information, not a defect to be quietly corrected in the file. To
change a number one re-runs the suite, not the artefact.
\end{principle}

\begin{principle}[A band failure halts; only extraction may be calibrated]
Failures split in two. A \emph{band} failure means the engine is wrong: work
stops and the cause is investigated. An \emph{extraction} failure means the
harness misread the result's shape: the check is corrected and the whole suite is
re-run. Fixing extraction is calibration, not gaming, only when the expected band
is left untouched.
\end{principle}

The bands are not decorative, and several of them encode a number whose value is
the point. Three rows make the discipline concrete. The first is an ordinary
positive result. The synchronous transfer-entropy row \method{ksg\_te} calls the
estimator on the USA and Japan series and checks the directed edge:

\begin{lstlisting}[language=JavaScript]
{ m: "ksg_te", p: { series: ["USA", "Japan"] }, async: true,
  expected: "USA->Japan full-sample KSG TE in [0.150,0.158] (verified 0.1542)",
  src: "A2 + #39 anchor",
  check: r => { const e = (r.edges || r.pairs || [])
      .find(x => /usa/i.test(x.from) && /japan/i.test(x.to)) || {};
    const v = num(e.te ?? e.TE);
    return { value: v, pass: inBand(v, 0.150, 0.158) }; } }
\end{lstlisting}

\noindent The last full run returned $0.154234$ for this edge, inside the band,
from a real job on the tower (\code{job\_20260612\_92fa3f31}); the worked trace in
Section~\ref{sec:worked} follows that exact call from HTTP request to single-JSON
response. The second is a degenerate negative that must \emph{stay} degenerate.
The \method{namh\_pipeline} row runs the full NAMH surrogate pipeline end to end
under a fixed seed and checks that, under the paper's own Benjamini--Hochberg
gate \citep{benjamini1995}, the network is empty:

\begin{lstlisting}[language=JavaScript]
{ m: "namh_pipeline",
  p: { n_surrogates: 200, window_index: 1, seed: 42, n_cores: 2 }, async: true,
  expected: "FDR retains 0/552 under the paper's own gate (degenerate, honest amber);
             raw te_mean in [-0.2242,-0.2222]",
  check: r => { const w = (r.per_window || [])[0] || {}; const f = w.fdr || {};
    const c = r.config || {};
    return { value: num(w.te_raw && w.te_raw.mean),
      pass: num(f.n_edges) === 0 && num(f.n_possible) === 552
            && w.degenerate === true
            && inBand(num(w.te_raw && w.te_raw.mean), -0.2242, -0.2222)
            && c.seed === 42 && c.rng === "L'Ecuyer-CMRG" }; } }
\end{lstlisting}

\noindent Here a \emph{populated} network would be the failure and the empty one
is the pass: the row insists on \textbf{0 of 552} directed edges retained in the
window, the window flagged \code{degenerate}, the raw window mean inside
$[-0.2242,-0.2222]$ (the last run returned $-0.22322165$), and the generator
pinned to L'Ecuyer's combined multiple-recursive scheme \citep{lecuyer1999} at
seed 42. The third is the live systemic-risk index. The \method{sri\_daily} row
recomputes the static-panel index in full from the stored panel and checks it
against a band one part in $10^{5}$ wide, $[0.00848, 0.00850]$, around the first
honest point $0.00849$ over 306 directed pairs. A reproduction target this tight
can only be met by re-running the same computation, which is the property the row
exists to certify.

The suite is honest about its own operational hazards, which is itself part of
the discipline. The runner rides out a Cloud Run cold start with a second,
longer health probe, because a single short probe once misreported a live engine
as unreachable while all rows passed; it waits politely under the engine's
rate limit rather than recording a self-inflicted red; and asynchronous rows are
either real tower jobs with persistent identifiers or honest \code{async\_pending}
placeholders, never fabricated values. The artefact records, per row, the
measured value, the elapsed milliseconds, whether the engine served it from cache,
and any job identifier, so that the run can be audited line by line.

\subsection{The nightly self-learning loop}
\label{sec:verification-loop}

The suite would be a static check were it not re-run. The centrepiece of the
verification layer is the loop in \file{scripts/nightly-loop.sh}, installed under
\code{cron} at \code{10 7 * * *} UTC, fifty minutes after the 06:00 UTC systemic-
risk tick. Its design intent is to survive a reboot, to be loud in the cron log
when something regresses, and never to silently repair a problem it should
surface. The cron entry and the script are installed and self-tested; at the time
of writing the loop has not yet completed an unattended run, so its cadence is
reported as configured rather than demonstrated. It re-arms the long-lived job
server only if its port is closed, killing
nothing, then runs the six steps summarised in Table~\ref{tab:loop} and pictured
in Figure~\ref{fig:loop}.

\begin{figure}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tikzpicture}[font=\footnotesize, node distance=5.5mm,
  st/.style={draw=cegrey, thick, rounded corners=2pt, fill=celight, align=center,
    inner sep=4pt, text width=2.05cm, minimum height=11mm},
  gate/.style={st, fill=ceorange!16, draw=ceorange},
  ar/.style={-{Stealth[length=2mm]}, thick, draw=cegrey}]
  \node[st]              (s1) {1.\ \code{run-evals}\\[1pt]\scriptsize real compute};
  \node[gate, right=of s1] (s2) {2.\ \code{state-refresh}\\[1pt]\scriptsize MEASURED $+$ DRIFT};
  \node[st, right=of s2] (s3) {3.\ \code{claims-refresh}\\[1pt]\scriptsize demote, never delete};
  \node[st, right=of s3] (s4) {4.\ \code{gen-report}\\[1pt]\scriptsize verbatim \LaTeX};
  \node[st, right=of s4] (s5) {5.\ \code{publish}\\[1pt]\scriptsize report gallery};
  \node[st, right=of s5] (s6) {6.\ \code{gap-proposals}\\[1pt]\scriptsize PI-gated};
  \foreach \a/\b in {s1/s2,s2/s3,s3/s4,s4/s5,s5/s6} \draw[ar] (\a)--(\b);
  \node[font=\scriptsize, text=ceorange, above=1mm of s2] {regression $\to$ exit 2};
  \node[font=\scriptsize, text=cegreen, below=4mm of s5.south]
    {steps 4--6: log-only, \code{nice -19}, zero compute (cannot re-trigger the hang)};
\end{tikzpicture}}
\caption{The six-step nightly loop. Step~2 governs the exit code, turning a
regression into a non-zero exit and a red dashboard; steps 4--6 do no computation,
so the reporting layer can never re-trigger a saturation. No step deletes a claim
or edits a result.}
\label{fig:loop}
\end{figure}

\begin{table}[t]
\centering
\small
\begin{tabular}{@{}c l p{0.62\textwidth}@{}}
\toprule
Step & Script & What it does, and how it stays honest \\
\midrule
1 & \file{run-evals.mjs} & Re-arms the job server (port-guarded, no kills), then runs the full suite, async rows as real tower jobs, writing a fresh \file{evals.json}. \\
2 & \file{state-refresh.mjs} & Measures live health, the eval summary, and the SRI feed; rewrites \emph{only} the \code{MEASURED} block of \file{STATE.md} and appends a dated \code{DRIFT} line on any regression. Its exit code is the loop's: non-zero means a problem line was written. \\
3 & \file{claims-refresh.mjs} & Re-verifies the mapped claims against the same night's artefact: a pass bumps \code{last\_verified}; a red marks the claim \code{contested} and inserts the other side of the pair. Never deletes. Log-only, so a database outage cannot repaint the night. \\
4 & \file{gen-compute-report.mjs} & Renders a LaTeX run report verbatim from \file{evals.json}; never recomputes, never invents, renders failures as loudly as passes. Run \code{nice -n 19} so it always yields to a tower job. \\
5 & \file{publish-reports.mjs} & Copies each report PDF and a thumbnail into the static report gallery and rewrites its manifest. Pure file copy, \code{nice}'d, non-fatal. \\
6 & \file{gap-proposals.mjs} & Mines the demand signals the engine exposes, applies the pre-registered rule, and emits PI-review candidate skeletons. Never auto-deploys. \\
\bottomrule
\end{tabular}
\caption{The six steps of \file{scripts/nightly-loop.sh}. Step~2 owns the loop's
exit code, so a regression is loud in the cron log; steps 4--6 are log-only and
non-fatal, so a rendering or reporting fault cannot mask the canary in steps
1--3.}
\label{tab:loop}
\end{table}

Two properties of the loop are worth drawing out. The first is the division of
authority between its steps. The eval suite and \method{state-refresh} are the
canary: \method{state-refresh} exits 2 on any regression -- the engine
unreachable, a failed eval, a changed method count, or a systemic-risk feed stale
beyond three weekdays -- and that exit code becomes the loop's, so a problem is
never silent. Everything downstream is deliberately log-only and non-fatal. A
BigQuery outage in the claims step, a LaTeX fault in the report step, or a missing
checkout in the publish step is recorded and skipped; none is allowed to repaint
a night whose real signal is the suite and the state ledger above it. The report
step is the one that can always yield, which is why it runs \code{nice -n 19}: it
is pure rendering plus a single \code{pdflatex} pass, and it must never contend
with a long-running tower job for the processor.

The second property is the one we hold to most firmly: the loop's own wiring is a
failable eval. A separate test, \file{evals/loop-integrity.test.mjs}, asserts
that the steps exist, that the artefact paths the steps pass to one another agree,
that the set of claims the refresher maps is a subset of the suite's rows, that no
step on the nightly path issues a delete, that the gap rule and its PI gate are
intact, and that the installed state is reported honestly. We record this as an
invariant because it is the load-bearing one.

\begin{invariant}[The verifier verifies itself]
\label{inv:self}
The self-checking loop is subject to the same standard as the methods it checks:
its wiring -- step existence, artefact-path agreement, the claims-to-evals
subset relation, the no-delete rule, and the pre-registered, PI-gated gap rule
-- is itself a pre-registered, failable test. The apparatus that asserts
correctness can therefore fail loudly when its own assumptions break.
\end{invariant}

\noindent That this is not a formality is visible in the test's history: its first
execution was red, eleven of twenty, and all of the failures were the harness
misreading shapes (a \code{m:} key written \code{method:}, a quoted path, a
\code{DELETE} appearing inside a comment). Those were extraction failures,
calibrated per the band-versus-harness rule with the bands untouched, and the
test then went green -- exactly the discipline the suite imposes on every other
row, now imposed on the loop itself.

\subsection{The learning ledger}
\label{sec:verification-ledger}

The engine keeps a single state file, \file{STATE.md}, with three blocks. The
\code{MEASURED} block is machine-written by \method{state-refresh} and is never
touched by hand; the \code{LEDGER} block is appended by working sessions; the
\code{LEARNING} block stages each burned lesson through a fixed lifecycle --
\emph{fail} (the lesson enters when something breaks), \emph{investigate} (the
cause is named), \emph{verify} (the fix is proven), and \emph{distill} (the lesson
is promoted to a consultable Skill). Thirteen learnings are recorded;
Table~\ref{tab:learnings} states each in a line.

\begin{table}[t]
\centering
\footnotesize
\begin{tabular}{@{}c l l p{0.50\textwidth}@{}}
\toprule
ID & Date & Stage & Lesson (terse) \\
\midrule
L1 & 2026-06-11 & distilled & A robustness grid must anchor through the paper's own scripts and estimation universe before any badge is written. \\
L2 & 2026-06-11 & distilled & Moving the engine root silently changes API-key resolution and can ship a chat-disabled revision; check the WARN line. \\
L3 & 2026-06-10 & distilled & Yahoo serves \code{close: null} for hours after a session; the finite-close guard makes the tick skip honestly. The schedule is the guard. \\
L4 & 2026-06-11 & distilled & Eval failures split into band failures (stop, investigate) and extraction failures (fix the check); calibration only with the band untouched. \\
L5 & 2026-06-11 & distilled & A documented tuple must name its full parameterisation or it is not a reproducible claim (the five-market panel). \\
L6 & 2026-06-08 & distilled & LaTeX source grep is insufficient for fact consistency; verify against the rendered PDF, including figure labels. \\
L7 & 2026-06-12 & distilled & A reboot killed both daemons mid-pipeline; long-lived services need a reboot-surviving re-arm, and pipelines should write artefacts as they go. \\
L8 & 2026-06-04 & distilled & Bibliography titles are looked up, never reconstructed from a codename; verify id, title, and authors against the registered record. \\
L9 & 2026-06-12 & verify & A dual-use script must guard its CLI dispatch with the main-module check, or an import can fire the wrong routine. \\
L10 & 2026-06-12 & verify & Grep a large vendored dependency's own source for exact symbol names before writing against it (the Lean proof compiled first try). \\
L11 & 2026-06-13 & verify & The 22-core hang had one cause: hard-coded \code{detectCores()-1} fan-out under concurrency; fixed by one server-set core ceiling with pinned BLAS. \\
L12 & 2026-06-13 & verify & GPU offload is feasible now with no install; the hung k-NN primitive ports to two CUDA kernels and is bit-exact to the FP64 CPU reference. \\
L13 & 2026-06-13 & verify & \method{ksg\_te} and \method{ksg\_robustness} now dispatch to the GPU, gated on the estimator's own output including its floating-point boundary quirk. \\
\bottomrule
\end{tabular}
\caption{The learning ledger \file{STATE.md} L1--L13. A lesson enters at
\emph{fail}, is named at \emph{investigate}, proven at \emph{verify}, and promoted
to a Skill at \emph{distill}.}
\label{tab:learnings}
\end{table}

Three of these are load-bearing for the systems story told elsewhere in this
paper. L11 is the resolution of the core-governance hang: two concurrent
robustness jobs each forked one worker per logical core, $2 \times 21$ workers
against unpinned multi-threaded linear algebra, and the fix was a single governed
budget -- one server-set core ceiling clamped last, with the BLAS thread count
pinned to one, applied at every parallel fan-out site. The pin is a determinism
gain as much as a stability one. L12 and L13 are the GPU bit-exactness bar: the
nearest-neighbour search that hung the workstation ports to two CUDA kernels, and
the gate insists the device \emph{equal} the CPU estimator rather than approximate
it. The non-obvious lesson distilled there is that one must gate on the
estimator's own output, including its floating-point boundary behaviour, not on
the textbook form of the estimator -- a one-dimensional neighbour count using
\code{findInterval} includes a boundary point that the absolute-difference form
excludes, and the gate caught it. Together these three turned an unbounded CPU
fork into a governed budget plus a bit-exact device offload, and each remains in
the ledger at \emph{verify} pending the gated promotion to a Skill.

\subsection{The claims ledger}
\label{sec:verification-claims}

Above the per-run artefact sits a slower record: what the engine takes itself to
know. The claims ledger is a BigQuery table whose schema is fixed in
\file{epistemic/schema.json}. Each row is one claim, with a stable
\code{claim\_id}; a \code{type} drawn from \{empirical, methodological, formal,
robustness, hole\}; a \code{statement} written in one paragraph including its own
limits; an \code{established\_at} and a nullable \code{last\_verified} timestamp;
a nullable \code{confidence} that carries a badge pass-rate where the claim is
badge-derived and is \code{NULL} otherwise, never invented; repeated
\code{conditions} and \code{counter\_conditions}; repeated \code{provenance\_ids}
so that every claim traces to a job, a badge, a file anchor, or a build; repeated
\code{paper\_refs}; and a \code{status} of \emph{established}, \emph{contested}, or
\emph{superseded}.

The ledger is seeded from verified ground truth alone by
\file{scripts/claims-seed.mjs}, which carries roughly twenty provenanced claims
and validates each against the schema before any write. The seeded set is
deliberately catholic about what counts as knowledge: it includes empirical
results (the USA-to-Japan transfer entropy; the Table-5-exact channel shares), a
formal claim (the closed spectral identity below), methodological claims (that the
live index shares only a name, not a validation, with the published systemic-risk
index), and \emph{holes} stated as claims about the programme's own gaps (that the
WaveQTE Stage-1 estimator is structurally unavailable in the image and the
engine's variant is a labelled reimplementation). Honest negatives and marked
holes are first-class rows, not omissions.

The lifecycle is the epistemic core. The nightly refresher
\file{scripts/claims-refresh.mjs} re-verifies the mapped claims against the same
night's artefact and obeys one rule above all others:

\begin{invariant}[The record demotes, it never deletes]
\label{inv:nodelete}
A passing eval bumps an established claim's \code{last\_verified}; a failing eval
marks the parent claim \code{contested} and inserts an auto-generated
contradiction as the other side of the pair, linked by a \code{contests:} provenance
id. Nothing on the nightly path is ever deleted. A contested row is not silently
re-greened by a later pass: only PI review resolves it, and the revision history
-- including a claim that was once contested and is now superseded -- is part of
the knowledge, not noise to be cleaned away.
\end{invariant}

\noindent The WaveQTE divergence is the worked instance of the full lifecycle. A
2026-02 working paper reports the financial channel dominant in the global
financial crisis at 50.0\%, while the engine's verified ground truth, the
published package reproduced to 0.000 pp, gives the trade channel dominant at
27.9\%. The claim was seeded \emph{contested}, with both sides recorded, then
\emph{superseded} once the investigation established that the two figures are
different estimands from different methods on different partitions, not a
contradiction. The superseded row ships; it is never deleted, and a separate
established claim records the resolution and links back to it. The claims are
exposed read-only over the kernel at \route{GET /api/claims} (and
\route{/api/claims/:id}), so the contested and superseded rows are publicly
visible and the record fabricates nothing when its backing store is briefly
unavailable.

\subsection{The formal layer}
\label{sec:verification-formal}

The thinnest and strictest layer is a formal one. The SOCH element rests on a
spectral identity: the squared modulus of the cascade transfer function equals a
product-Lorentzian spectrum. We close that identity in Lean~4 against mathlib, as
the proposition \code{prop:spectrum},
\[
  \Norm{H(\omega)}^{2} = S(\omega),
\]
machine-checked unconditionally. The continuous-integration check is a green
\code{lake build}; the reproduce page greps the Lean source and fails on drift, so
the public count and the source stay in lockstep. The stationary-point half of the
companion peak lemma is also fully accepted: the first-order condition is shown
equivalent to a cubic in $\omega^{2}$, the symmetric peak is located at
$\omega^{\ast} = \alpha/\sqrt{3}$, and exactly one positive stationary frequency
is shown to exist and to lie in a stated bracket.

What we will not do is dress the layer as more complete than it is. The analytic
half of the peak lemma -- that the maximiser of $\omega \, S(\omega)$ exists and
satisfies the first-order condition -- remains stated, not proved.

\begin{invariant}[A \texttt{sorry} is never reported as a proof]
\label{inv:sorry}
The formal layer carries an honest \code{sorry}-count of \textbf{1 of 12}
declarations. The single open obligation is named and its route is documented in
the source; it is never presented as closed, and the public count is held to the
source by the same lockstep check that gates every other figure.
\end{invariant}

\noindent This is the same posture as the rest of the section, applied to
machine-checked mathematics rather than to a numerical band. A closed identity is
reported as closed because a proof assistant accepted it; an open obligation is
reported as open because none did. The four artefacts -- the failable suite, the
self-checking loop, the demoting claims record, and the honestly counted proof
-- are one mechanism seen at four time-scales, and the property they share is the
one the project exists to demonstrate: every figure the engine states is a figure
the engine can be seen to fail.
