\section{The Elements}
\label{sec:elements}

The engine is the vehicle; the elements are what it carries. Six published
frameworks have come out of the group, and it would be possible to read each as
a self-contained study with its own codebase. We read them instead as elements
of one programme: distinct economic questions, answered by distinct
configurations of the same eight-primitive substrate, certified by the same
failable gate, and re-runnable through the same engine. The substrate primitives
are long-memory estimation, the maximal-overlap discrete wavelet transform
(MODWT), transfer entropy, surrogate generation by the iterated amplitude-adjusted
Fourier transform (IAAFT), community detection, network formation, structural
channel attribution, and receiver-operating-characteristic (ROC) evaluation.
Each element below states the economic question it asks, the primitives it
instantiates, its headline verified result, and its honest status. The numbers
are quoted exactly as the verified record holds them; where a figure is not in
that record we mark it rather than supply one.

Four of the six elements measure the flow of information between markets, and the
economics says they should find something to measure. The Grossman--Stiglitz
argument \citep{grossman1980} implies that informationally efficient markets are
impossible, so a residue of costly, privately held, unequally distributed
information must persist; transfer entropy is the programme's instrument for
tracing the flow of exactly that residue, directionally and across scales. A
reading caution applies throughout. These markets are adaptive and heterogeneous
\citep{lo2004}, so a structure measured in one regime need not persist into the
next, and several elements below report exactly such a dissolution or a
knife-edge. We treat those as findings, not as failures of the apparatus.

\subsection{NAMH: adaptive market networks}
\label{sec:elem-namh}

\paragraph{Question.} Do equity markets form a directed information network whose
broadcasters and receivers can be identified, and is that structure stable as the
network adapts over two decades? This is the network reading of the adaptive
markets hypothesis \citep{lo2004}: efficiency as an evolving, relational property
rather than a fixed one. The economic stake is whether information leadership in
the global equity system is persistent and locatable, or whether it migrates as
participants adapt; an answer that holds across twenty years of windows is an
answer about structure, while one that dissolves is itself a statement about
adaptation.

\paragraph{Primitives.} Long-memory estimation (a Hurst exponent per market),
transfer entropy for the directed edges, IAAFT surrogates and false-discovery
control for edge significance, and network formation with directed centrality
(out-strength, in-strength, PageRank, Katz, eigenvector) read on the resulting
graph.

\paragraph{Result.} The FRONTIERS Paper~I treatment, a seventeen-page study over
twenty-eight assets from 2001 to 2026, finds that the United States broadcasts
and Japan receives. The United States leads on out-strength in $9$ of $20$
windows annually and $26$ of $79$ quarterly; Japan receives, leading on
in-strength in $12$ of $20$ windows, on PageRank in $10$ of $20$, and on Katz
centrality in $8$ of $20$ \citep{bhandari2026econstellar,namhpkg}. On the engine,
the NAMH transfer-entropy estimators run through the paper's own \code{namh}
package: the window-mean transfer entropy is $-0.22322165$, inside its
pre-registered band, and reproduces against the cached run to a maximum absolute
deviation of $1.55\times10^{-15}$.

\paragraph{Honest status.} Two honesty markers belong on the record. First, the
broadcaster/receiver reading carries an exception, stated rather than smoothed:
the quarterly Katz leader is Argentina with $22$ edges, narrowly over Japan's
$21$. Second, on the engine the false-discovery-controlled NAMH network is
degenerate: $0$ of $552$ candidate edges survive the gate, and we report that as
a degenerate network rather than relaxing the threshold to manufacture structure.
The headline ranks above are magnitude-ordered centralities; the FDR result is a
separate, stricter question, and the two are kept distinct.

\subsection{SOCH: scale-ordered contagion}
\label{sec:elem-soch}

\paragraph{Question.} Does cross-border contagion have a spectral signature, an
ordering across time scales that reflects how heterogeneous participants adapt to
information at different horizons? SOCH formalises that ordering and asks whether
it holds in the data. The economic motivation is that a high-frequency trader and
a pension fund respond to the same shock on different clocks, so contagion that
looks alike in aggregate may be ordered by scale once it is decomposed; recovering
that order distinguishes fast, mechanical transmission from slow, fundamental
adjustment.

\paragraph{Primitives.} MODWT to resolve a relationship by scale, transfer
entropy within each scale band for the directed contagion profile, IAAFT
surrogates for significance, and a spectral-density construction that the formal
layer machine-checks.

\paragraph{Result.} On the engine the scale-resolved contagion profile from the
United States to India aggregates to $0.0391$ over four scales, peaking at scale
\code{d4}, computed through the published \code{sochcontagion} package
\citep{bhandari2026soch,sochpkg}. The robustness badge holds the baseline cell
($\tau=0.05$, four filter orders) across all $28$ market pairs and returns an
overall pass rate of $0.9911$ ($111$ of $112$ grid cells), under a seeded null.
The spectral theory is supported by a formal layer: of twelve Lean~4
declarations, eleven are machine-accepted, including the unconditional closure of
the product-Lorentzian spectral-density proposition,
$\Norm{H(\omega)}^2 = S(\omega)$.

\paragraph{Honest status.} The framework's three pre-registered significance
tests do not all clear. SOCH-A is significant at $p=0.042$ and SOCH-B holds
$28/28$, but \textbf{SOCH-C is not significant, at $p=0.105$}, and we treat that
as an immutable fact of the record rather than a result to be managed. The formal
layer is likewise reported as it stands: the single unproved declaration, the
analytic half of the peak-location lemma, honestly carries a \code{sorry}
(sorry-count $1/12$), and a \code{sorry} is never reported as proved.

\subsection{Contagion channels}
\label{sec:elem-channels}

\paragraph{Question.} When contagion crosses a border, through what does it
travel? The framework identifies and attributes cross-border transmission to
structural channels (trade, finance, and others) rather than measuring only that
transmission occurred. The distinction matters for policy: a shock that
propagates through the trade channel calls for a different response than one
carried by financial linkages, and an attribution that does not name the channel
leaves the question that policy actually asks unanswered.

\paragraph{Primitives.} Channel attribution as the central primitive,
decomposing a transmission measure across structural channels, supported by the
network and connectedness machinery that supplies the transmission edges and by
episode partitioning across crises.

\paragraph{Result.} Across eight crisis episodes the framework attributes the
dominant share of global-financial-crisis contagion to the trade channel at
$27.9\%$, with an interval of $[26.1, 29.8]$
\citep{bhandari2026contagion,ccpkg}. On the engine the attribution runs through
the published \code{contagionchannels} package and reproduces the trade share to
$0.000$ percentage points against the archived decomposition. This is the cleanest
reproduction in the programme: the engine's live number equals the paper's to the
reported precision.

\paragraph{Honest status.} The trade share is a contested figure across method
and partition, and is carried as such (see WaveQTE below); the engine's
contribution is to make the canonical $27.9\%$ re-runnable to the digit, not to
adjudicate the contest.

\subsection{WaveQTE: wavelet quantile transfer}
\label{sec:elem-waveqte}

\paragraph{Question.} How does tail risk transfer between markets across both
time scale and quantile, and how much of an episode's contagion does a
wavelet-quantile reading attribute to a given channel? The economic interest is
in the tails specifically: ordinary co-movement and crisis co-movement are
different objects, and a method resolved by quantile asks how transmission behaves
when it matters most rather than on average.

\paragraph{Primitives.} MODWT for the scale resolution and quantile transfer
estimation for the tail-dependent directed flow, with the same surrogate and
network primitives downstream.

\paragraph{Result.} A wavelet-quantile reading attributes $50.0\%$ of the
relevant episode's contagion where the structural channel decomposition of
Section~\ref{sec:elem-channels} attributes $27.9\%$. On the engine, the
\code{wqte} method returns a United-States-to-India quantile transfer of $0.039$
at $\tau=0.05$, an aggregate that sits inside its pre-registered band.

\paragraph{Honest status.} The $50.0\%$-versus-$27.9\%$ gap was investigated and
resolved, and the resolution is itself the finding: \textbf{it is a
method-and-partition divergence, not a bug.} The two figures come from different
estimators (a wavelet-quantile activation-scoring reading against a structural
instrumental-variables decomposition) over different episode partitions, so they
are measuring related but distinct quantities and are expected to differ. One
further honesty marker: the framework's packaged Stage-1 estimator is
structurally unavailable inside the deployed image, so the engine's \code{wqte}
is an honest MODWT-plus-quantile-regression reimplementation, declared as such,
rather than a call into the original Stage-1 code. It is banded like any other
method and is not presented as the packaged estimator.

\subsection{Commodity systems}
\label{sec:elem-commodity}

\paragraph{Question.} How does the commodity complex fragment and re-form across
crises, and which episode leaves it most fragmented? The object is the network of
commodities itself, read as a system that reorganises under stress. The economic
content is the integration of the commodity complex: a complex that fragments
under a crisis offers diversification exactly when other markets are
co-moving, so locating the deepest fragmentation locates the episode in which the
complex behaved least like a single asset.

\paragraph{Primitives.} Network formation over the commodity cross-section,
community detection to recover the cluster structure, and a fragmentation measure
read across crisis episodes.

\paragraph{Result.} Over twenty-three commodities from 1991 to 2025, the Subprime
crisis leaves the complex most fragmented, with a fragmentation coefficient of
magnitude $\Norm{\text{FC}} = 0.290$ and a partition into five communities. The
finding is that the deepest fragmentation of the commodity network in this sample
sits at the Subprime episode rather than at a later crisis.

\paragraph{Honest status.} The fragmentation magnitude and community count are
the verified figures; finer claims about which commodities migrate between
communities are governed by the published study's own community-structure record
and are not restated here beyond what the verified record holds. Where a
cross-episode comparison would need per-episode fragmentation coefficients beyond
the Subprime magnitude, figures the verified record does not carry, we leave them
unstated rather than assert them.

\subsection{MCPFM: protocol-mediated systemic risk}
\label{sec:elem-mcpfm}

\paragraph{Question.} Can a protocol-mediated, multi-scale network model of the
financial system forecast systemic-risk episodes, and does that forecasting
ability survive a pre-registered re-evaluation? This is the element where the
programme tests one of its own models against an out-of-sample, honestly scored
benchmark. The economic claim under test is strong, that network structure
carries predictive content about systemic stress, and the value of testing it
under pre-registration is precisely that the apparatus cannot quietly retreat to
the sample and episode where the claim looks best.

\paragraph{Primitives.} The full network and connectedness stack feeding a
multi-scale systemic-risk construction, with ROC evaluation as the primitive that
scores the forecasts, here read through the area under the curve and a formal
test of predictive superiority.

\paragraph{Result.} In its first evaluation the model returns an area under the
ROC curve of $0.581$ (DeLong $p=0.030$) over the full sample, rising to $0.915$
on the United States during the COVID episode \citep{bhandari2025mcpfm}. A
\emph{pre-registered} second-version re-evaluation then returns an area under the
curve of $0.470$ with a Hansen superior-predictive-ability $p=0.031$, and is
reported openly.

\paragraph{Honest status.} This is the programme's sharpest negative.
\textbf{The pre-registered v2 re-evaluation returns AUC $0.470$}, below the $0.5$
chance line, and we report it as such rather than retreating to the favourable v1
figures. The pre-registration is what gives the negative its force: the test was
fixed before the run, so a result below chance is a result, not a discard. The
reproduction status of the systemic-risk index is carried as honest-pending,
consistent with the rest of the programme's reproduce discipline.

\subsection{Cross-framework consistency}
\label{sec:elem-consistency}

Read together, the six elements are not six tools but six configurations of one
substrate, and that is the claim the engine makes good. The same long-memory
estimator that gives NAMH its per-market Hurst exponents is the estimator the
engine bands as \code{namh\_hurst}; the same KSG/Frenzel--Pompe transfer-entropy
kernel supplies NAMH's directed edges, SOCH's within-scale contagion, and the
engine's headline United-States-to-Japan flow of $0.154234$; the same MODWT
resolves SOCH and WaveQTE by scale; the same IAAFT surrogates and false-discovery
control gate significance across NAMH, SOCH, and WaveQTE; the same network and
community-detection machinery recovers structure for NAMH, the commodity complex,
and MCPFM; and the same channel-attribution primitive that the contagion-channels
element reproduces to $0.000$ percentage points is the one whose method-dependence
the WaveQTE divergence illustrates. Verifying a primitive therefore verifies it
for every element that instantiates it, which is the economy the programme
framing is meant to buy: twenty-six checked methods carrying six frameworks,
rather than six codebases asserting their own numbers in parallel.

Table~\ref{tab:elements-matrix} lays the six elements against the eight primitives.
The filled columns for transfer entropy and network connectedness show how few
independent estimators carry the whole programme.

\begin{table}[t]
\centering
\small
\setlength{\tabcolsep}{4.5pt}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{@{}l*{8}{c}l@{}}
\toprule
\textbf{Element} & P1 & P2 & P3 & P4 & P5 & P6 & P7 & P8 & \textbf{Headline (verified)} \\
\midrule
NAMH & \textcolor{ceblue}{\textbullet} & & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & & & US out-strength 9/20 \\
SOCH & & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & & & & & & SOCH-C $p=0.105$ (n.s.) \\
contagion-channels & & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & & \textcolor{ceblue}{\textbullet} & & \textcolor{ceblue}{\textbullet} & & trade $27.9\%$ \\
WaveQTE & & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & & & & & \code{wqte} $0.039$ \\
commodity & & & \textcolor{ceblue}{\textbullet} & & \textcolor{ceblue}{\textbullet} & \textcolor{ceblue}{\textbullet} & & & $|FC|\;0.290$ \\
MCPFM & & \textcolor{ceblue}{\textbullet} & & & & \textcolor{ceblue}{\textbullet} & & \textcolor{ceblue}{\textbullet} & v2 AUC $0.470$ \\
\bottomrule
\end{tabular}
\caption{The six elements against the eight substrate primitives: P1 long memory,
P2 MODWT wavelets, P3 transfer entropy, P4 surrogates, P5 community detection,
P6 network connectedness, P7 channel attribution, P8 ROC/DeLong. A marker
indicates the element instantiates that primitive (the principal-primitive view
of Figure~\ref{fig:substrate}); the final column gives one headline verified
figure per element, positive and negative alike.}
\label{tab:elements-matrix}
\end{table}
