\section{The learning ledger}
\label{app:learnings}

The engine keeps a staged record of operational lessons in \file{STATE.md}: a
burned lesson enters at \emph{fail}, \emph{investigate} names the cause,
\emph{verify} proves the fix, and \emph{distil} promotes it to a consultable
skill that future sessions read before acting. This is the machinery by which the
system learns from its own failures rather than repeating them. We reproduce the
ledger below in condensed form; each row is a real incident with a named cause
and a verified fix.

\renewcommand{\arraystretch}{1.3}
\footnotesize
\begin{longtable}{@{}p{0.7cm}p{1.6cm}p{11.4cm}@{}}
\toprule
\textbf{ID} & \textbf{Stage} & \textbf{Lesson} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Stage} & \textbf{Lesson} \\
\midrule
\endhead
\midrule
\multicolumn{3}{r@{}}{\textit{continued on next page}} \\
\endfoot
\bottomrule
\endlastfoot

L1 & distilled & A pre-registered robustness grid must anchor through the paper's own scripts and estimation universe before any badge is written: the package-default universe gave $p\,0.158$ where the published 56-pair design gives $0.042$. Stop on anchor failure, document the amendment openly, keep the auxiliary run. \\
L2 & distilled & \file{cloudrun/deploy.sh} resolves the API key from env first, then \code{\$REPO/../.env.local}; moving the engine root silently ships a chat-disabled revision. Check the WARN line; restore with \code{gcloud run services update --update-env-vars} (no rebuild). \\
L3 & distilled & Yahoo serves \code{close: null} for ten hours after a session; the finite-close guard makes the 06:00Z tick skip honestly and composition heals the gap next day. Never fire the SRI tick manually during the US session: the schedule \emph{is} the partial-bar guard. \\
L4 & distilled & Eval failures split into band failures (engine wrong: stop, investigate) and extraction failures (harness misread the result shape: fix the check, re-run the whole suite). Fixing extraction is calibration, not gaming, only while the expected band is untouched. \\
L5 & distilled & ``5-market IPS $-77.26$'' was unreproducible until the market set was pinned to $\{$India, USA, UK, China, Japan$\}$; a different fifth market gives $-80.16$. Documented tuples must name their full parameterisation or they are not reproducible claims. \\
L6 & distilled & LaTeX source grep is insufficient for count consistency: TikZ figure labels and line-wrapped phrases are invisible to line-based search but visible in the rendered PDF. Verify with \code{pdftotext file - | tr} newline \code{space | grep}, ligature-tolerant, across all figure sources. \\
L7 & distilled & A laptop reboot killed both \code{setsid} daemons mid-pipeline; the eval suite survived because it had already written its artefact. Long-lived local services need a reboot-surviving re-arm; pipelines should write artefacts as they go, not at the end. \\
L8 & distilled & Bibliography titles are looked up, never reconstructed from codenames: ``MCPFM'' resolves to a Model Context Protocol title (arXiv:2507.08065), not the codename expansion. Verify id $\leftrightarrow$ title $\leftrightarrow$ authors against the registered record before citing. \\
L9 & verify & A dual-use ESM script (CLI $+$ importable) must guard its CLI dispatch with the main-module check: a seeder's top-level dispatch ran the wrong selftest and \code{process.exit}'d, masquerading as a pass. Fixed and selftested. \\
L10 & verify & Before writing code against a large vendored dependency, grep the dependency's own source for exact symbol names first: the Lean spectral proof compiled first-try with zero name-risk iterations because the mathlib symbols were verified from source pre-write. The code-API corollary of L8. \\
L11 & verify & The 22-core hang had one named cause: three runners hard-coded \code{detectCores()-1} ($=21$ workers), ignoring the job's \code{n\_cores}; two concurrent jobs forked $2\times21$ workers over unpinned BLAS. Fix: one governed budget \code{ce\_ncores()} with a server-set hard ceiling on all six fan-out sites, BLAS pinned to 1. Parallel fan-out must be governed by a ceiling, never by \code{detectCores()} under concurrency. \\
L12 & verify & GPU offload is feasible with zero install: \code{numba} 0.63.1 $+$ CUDA 12.4 are present and the RTX 3000 Ada is supported. The k-NN transfer-entropy search ports to two \code{numba.cuda} kernels, bit-exact against the FP64 CPU reference, 32--74$\times$ faster. The bar held: the GPU must equal the CPU, not approximate it. \\
L13 & verify & \code{ksg\_te} and \code{ksg\_robustness} dispatch to the GPU with governed-CPU fallback (default AUTO; \code{CE\_GPU=0} forces CPU). The bit-exactness gate caught a non-obvious boundary convention in the engine's own 1-D count, which the GPU then replicated host-side. Gate on the estimator's own output, including its floating-point boundary quirks, not the textbook form. Full-panel re-run: 35.6 min on one core; the 22-core saturation is gone. \\
\end{longtable}
\normalsize
\renewcommand{\arraystretch}{1.0}

\noindent
The distilled rows (L1--L8) have been promoted to named skills that future
sessions consult before acting; the verify-stage rows (L9--L13) carry a verified
fix and are pending distillation. The ledger's own structural wiring (its steps
exist, its artefact paths agree, the claims map is a subset of the suite rows, no
nightly step deletes, the gap rule and its review gate remain intact) is itself a
failable evaluation, \file{evals/loop-integrity.test.mjs}, which began at 11/20
red and now passes.
